An Empirical Analysis of C Preprocessor Use

### 2000-01-18 macros/papers/emp-use-2.tex
Update the date, remove "Technical Report UW-CSE-97-04-06".

% Delete in final version of paper.
\newcommand{\comment}[1]{\textbf{[[#1]]}}
% Delete above in final version of paper

@@

\date{Revision of Technical Report UW-CSE-97-04-06 (original date April 22, 1997) \\
Department of Computer Science and Engineering \\
University of Washington \\
Box 352350, Seattle, WA  98195-2350  USA \\
{\small \{{\tt mernst},{\tt gjb},{\tt notkin}\}{\tt @cs.washington.edu}} \\
31 March 1999}

>>>>

% % Delete in final version of paper.
% \newcommand{\comment}[1]{\textbf{[[#1]]}}
% % Delete above in final version of paper

@@

\date{% Revision of Technical Report UW-CSE-97-04-06 (original date April 22, 1997) \\
Department of Computer Science and Engineering \\
University of Washington \\
Box 352350, Seattle, WA  98195-2350  USA \\
{\small \{{\tt mernst},{\tt gjb},{\tt notkin}\}{\tt @cs.washington.edu}} \\
18 January 2000}
